Consumption and resistance across states and HRRs

### 2017-03-02 chronic-conditions/chronic-condition-drivers.Rmd
cleaning up Rmds

---
title: "What chronic conditions are associated with increased antibiotic consumption?"
author: "Scott Olesen"
date: "2/27/2017"
output: html_document
---

@@

I'll use the Medicare 2011 data.

@@

>>>>

---
title: "Chronic conditions and increased antibiotic consumption"
author: "Scott Olesen"
date: "2/27/2017"
output: html_document
---

@@

I'll use the Medicare 2011 data with normal filters (age 65 or above, only beneficiaries on Medicare for 12 months of the year).

@@

As a verification, I'll look at the distribution of number of claims among patients who have COPD or not. The mean for patients with COPD is more than double than that for patients without, which makes the age-adjusted 2.23 fold increase seem reasonable.

```{r copd}
usage_summary %>%
  mutate(has_copd=COPD==3) %>%
  group_by(has_copd) %>%
  do(summary(.$n_claims) %>% tidy) %>%
  kable
```

### 2017-03-02 inequality/consumption-inequality.Rmd
cleaning up Rmds

@@

@@

@@

Surprisingly, the characteristics of the beneficiaries are fairly constant by consumption $n$-tile among those who took antibiotics. Those who took no antibiotics where more male and less white.

>>>>

```{r inequality_cumrelfreq}
normalize = function(x) x / max(x)
usage %>%
  group_by(bene_id) %>%
  summarize(n_claims=sum(n_claims)) %>%
  arrange(n_claims) %>%
  mutate(cdf_x=cume_dist(n_claims), cdf_y=normalize(cumsum(n_claims))) %>%
  group_by(cdf_x) %>%
  summarize(cdf_y=max(cdf_y)) %>%
  ggplot(aes(x=cdf_x, y=cdf_y)) +
  geom_point() + geom_line() +
  xlab('cumulative fraction of beneficiaries') +
  ylab('cumulative fraction of claims') +
  xlim(0, 1) + ylim(0, 1) +
  theme_minimal()
```

@@

These results all show inequalities measured using number of days.

@@

As expected, greater consumption is correlated with greater age and comorbidity. There are strange trends among gender and race (higher consumption is associated with more female and more white until 10--20 claims, after which point those trends reverse).

@@

### 2017-03-02 states/resistance/state-report.Rmd
cleaning up Rmds

I used the 2011 Medicare data.

@@

## Coherence of bug/drug combinations in resistance data

To ensure coherence, I only use the bug/drug combinations that appear in antibiograms in at least 20 states. This is equivalent to filtering those bug/drug combinations that have at least 125 records.

@@

Linear models:

end linear models

@@

@@

**swo adjust** The results from the HRR level differ: both identified a relationship between *E. coli* and cipro and MSSA and azithromycin. However, the state-level data  identified a negative relationship between MRSA and Bactrim while the HRR data identified a negative relationship between *K. pneumoniae* and Bactrim. The state-level data also identified *S. pneumoniae* and azithromycin.

@@

#### Linear

>>>>

I used the 2011 Medicare data. To ensure coherence, I only use the bug/drug combinations that appear in antibiograms in at least 20 states. This is equivalent to filtering those bug/drug combinations that have at least 125 records.

@@

@@

@@

#### State-level resistance-averaged correlations using linear models

@@

@@

#### State-wide consumtion, all-antibiogram using linear models
